### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: wording, typos

\begin{definition}
  We say that set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exists a distinguished initial identifier $e_0 \in \eventSet$;
    \item there exists a function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

We will encode the event structure as a tuple 
$\tup{\eventSeq, \lLAB, \lfPO, \lfRF}$, 
below we explain the meaning of each component, 
and how they together form a prime event structure.

>>>>

\begin{definition}
  We say that a set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exists a distinguished initial identifier $e_0 \in \eventSet$;
    \item there exists a function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

We will encode the event structure as a tuple 
$\tup{\eventSeq, \lLAB, \lfPO, \lfRF}$ and explain
below the meaning of each component, 
and how they form a prime event structure together.

### 2021-04-08 papers/SYRCoSE/regmachine.tex
Regmachine: wording, typos

The semantics is given in the form of a
\emph{labelled transition system}~%
\footnote{As we have mentioned, in our \coq development we actually use 
the monadic encoding of the operational semantics. 
The labelled transition system can be derived from this encoding.}
State of the system consists of instruction pointer
and a map from registers to their values, 
as shown in \cref{fig:regmachine-thrdstate}. 
The rules of the semantics are standard 
(see \cref{fig:regmachine-thrdsem}).

@@

  s          &\in& \ThrdState    &::=& \tup{\ip{i}, \regmap} &                         \\
  \ip{i}     &\in& \N            &   &                    & \text{instruction pointer} \\
  \regmap    &\in& \Reg \fun \Z  &   &                    & \text{registers mapping}   \\

>>>>

The semantics is given in the form of a
\emph{labelled transition system}~%
\footnote{As we have mentioned, in our \coq development we actually use 
the monadic encoding of the operational semantics. 
The labelled transition system can be derived from this encoding.}.
The state of the system consists of an instruction pointer
and a map from registers to their values, 
as shown in \cref{fig:regmachine-thrdstate}. 
The rules of the semantics are standard 
(see \cref{fig:regmachine-thrdsem}).

@@

  s          &\in& \ThrdState    &::=& \tup{\ip{i}, \regmap} &                         \\
  \ip{i}     &\in& \N            &   &                    & \text{instruction pointer} \\
  \regmap    &\in& \Reg \fun \Z  &   &                    & \text{register mapping}   \\
